---
title: "Project2 Pt2 Analysis"
author: "Rohini"
date: "12/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## A tutorial for my_rf_cv

```{r}
library(dplyr)
library(ggplot2)

data <- read.csv("../Data/my_penguins.csv") %>% na.omit() %>%
    select(bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g)

rf_cv_function <- source("../Code/my_rf_cv.R")$value

k_vals <- c(2,5,10)
cv_sd <- c()
cv_means <- c()
all_statistics <- data.frame(matrix(NA, nrow = 30, ncol = 3))
for (i in 1:3) {
  MSE_vals <- c()
  for (j in 1:30) {
    cv_val <- rf_cv_function(data, k_vals[i])
    MSE_vals <- append(MSE_vals, cv_val)
  }
  cv_sd <- append(cv_sd, sd(MSE_vals))
  cv_means <- append(cv_means, mean(MSE_vals))
  all_statistics[,i] <- MSE_vals
}

colnames(all_statistics)<- c("k2","k5","k10")

boxplots <- ggplot() + 
  geom_boxplot(all_statistics, mapping=aes(x=2, y=k2)) +
  geom_boxplot(all_statistics, mapping=aes(x=5, y=k5)) + 
  geom_boxplot(all_statistics, mapping=aes(x=10, y=k10)) +
  labs(x="K neighbors", y="Error", title="Cross Validation Error by Random Forest")
boxplots

ggsave(
  "boxplots.png",
  path = "../Output/Figures"
)

summary_stats <- data.frame(k_vals, cv_means, cv_sd)
saveRDS(summary_stats, file="../Output/Results/summary_stats.rds")
write.csv(all_statistics, file="../Output/Results/all_cv_values.csv")
```
From these results we can see that a higher number of k leads to a lower standard deviation. This means there is less variability within the estimate output data. In the boxplots we can also see that the third model is more "evenly" spread across a smaller range while the other two models have a much wider range. From this we can infer that a larger value of k delivers more precise results (remember, precision is not equal to accuracy).
